%!TEX program = xelatex

\documentclass[11pt,titlepage]{report}
\input{../../library/import}
\input{../../library/style}
\addbibresource{../../library/bibliography.bib}

\begin{document}

Appendix~\ref{app:sig-an} contains an in-depth analysis of ASK and FSK signaling whose results will assumed to be known and expected here. Also, we obtained a lot of measurement results. We only appended the relevant results.

\paragraph{ASK} According to our expectations, the amplitude of the PSD decreased as we decreased the modulation index. When we changed the carrier frequency, the PSD shifted accordingly, which means we observed a delta pulse at the carrier frequency with the PSD of the modulation signal centered around it. However, when we changed the bit rate, the change of bandwidth was hard to observe and we mainly observed the decrease in amplitude of the PSD. This could be due to the fact that only a signal of short duration is evaluated, for which its PSD had not fully converged to its expected form. The measurement results of altering the bit rate on an ASK signal are shown in Appendix~\ref{app:res}.

\paragraph{FSK} As we changed the frequency deviation $\Delta F$, the delta pulses and PSD changed according to our calculations. This means that we among other things observed delta pulses at $f_c\pm \Delta F$, where $f_c$ denotes the carrier frequency. Also, we observed the expected shift of the PSD when we changed the carrier frequency. Furthermore, we observed the same behaviour for changes to the bit rate as for ASK.

In all measurements we encountered the expected sinc-like behaviour which originates from the used binary modulation signals.

The only abnormality we observed, was the presence of delta pulses in the PSD at multiples of the signal frequencies. These peaks can also be observed in Appendix~\ref{app:res}. The distance between the sender and receiver was approximately between \SI{10}{cm} and \SI{20}{cm}. As half the wavelength of the used signals is in the range of $\lambda/2=v/2f\approx 343/2000\approx\text{\SI{17}{cm}}$, these delta pulses could very well correspond with standing waves which originate from the reflecting behaviour of waves.

The significant difference we noticed in our calculations and observations was that the PSD of an ASK contains a delta pulse and a copy of the spectrum of the modulation signal centered around the carrier frequency, while the PSD an FSK contains both centered around $f_c\pm \Delta F$.

\end{document}