%!TEX program = xelatex

\documentclass[11pt,titlepage]{report}
\input{../../library/import}
\input{../../library/style}
\addbibresource{../../library/bibliography.bib}

\begin{document}

\chapter{Assignment 2}
\section{Task 1}
Let us consider the case of a transmission line with unknown length. If we terminate the transmission line with a load $Z_l$, then, for a measurement $i$, if $\beta_i=2 \pi f_i \gamma$, the input impedance is given by

\begin{align}
	Z_{in,i}(l)=Z_0\frac{Z_l+j Z_0 \tan{(\beta l)}}{Z_0+j Z_l \tan{(\beta l)}}.
\end{align}

Solving for $l$ yields

\begin{align}
	p_i &= \frac{Z_0 Z_l - Z_{in,i} Z_0}{Z_{in,i} Z_l - Z_0^2}, \\
	q_i &= \frac{1+p_i}{1-p_i}, \\
	a_i &= \frac{\operatorname{Arg}(q_i)}{ 2\beta_i} \in \mathbb{R}, \\
	b_i &= \frac{\pi}{\beta_i} \in \mathbb{R}, \\
	c_i &= -\frac{-\operatorname{ln}|q_i|}{2 \beta_i} \in \mathbb{R}, \\
	l &= a_i + b_i k_i + c_i j \text{ where } k_i \in \mathbb{Z}.
\end{align}

If we consider a real-world sitation, then the length of the cable should be real. Therefore, $l=a_i+b_i k_i \in \mathcal{L}_i$. Obviously, this corresponds to infinitely many cable lengths, which is not what we wanted. Using two measurements $\mathcal{L}_1$ and $\mathcal{L}_2$ with different frequencies, one could determine $\mathcal{L}_1 \cap \mathcal{L}_2 = \mathcal{L}_3$ to reduce the number of solutions. If $|\mathcal{L}_3|=1$, then we have uniquely determined the length. However, this will most certainly be not the case, as we are dealing with periodic functions. By using the common period of $\tan{(\beta_1)}$ and $\tan{(\beta_2)}$ in combination with the spacing between the solutions in that period, one can determine an unambiguous range.

%However, if $\beta_{1} l \neq \beta_{2} l + k \pi$, $k \in \mathbb{Z}$, then one can show that $|\mathcal{L}_3|=1$ and determine the actual cable length.

\section{Task 2}
Let us consider the case in which we have three finite sets $\mathcal{L}_1$, $\mathcal{L}_2$ and $\mathcal{L}_3$ whose elements have insufficient accuracy, which means that $\mathcal{L}_1 \cap \mathcal{L}_2 \cap \mathcal{L}_3 = \emptyset$, and we want to guess the cable length. This means we want to find a $y \in \mathcal{L}_1 \cup \mathcal{L}_2 \cup \mathcal{L}_3$ for which $\epsilon(y)$ is minimal, where

\begin{equation}
	e(x) = |x-a|+|x-b|+|x-c|
\end{equation}

for some $a \in \mathcal{L}_1$, $b \in \mathcal{L}_2$ and $c \in \mathcal{L}_3$. Lets say we are able to determine a $a$ for which $|a-b|$ and $|a-c|$ is minimized. Then $e(a)=|a-b|+|a-c|$, which we just minimized! This means that $a=y$.

If we use an algorithm which operates the way we just described, we are able to determine $y$ in linear time ($\operatorname{O}(n)$). Using $a = a_1 + b_1 k_1$, then a $b$ for which $|a-b|$ is minimal is given by

\begin{equation}
	b=a_2+b_2 \operatorname{round}\left(\frac{a-a_1}{b_1}\right).
\end{equation}

This can easily be proved using linearity. We calculated the length of the cable \SI{1.2500}{m}. Appendix~\ref{app:matlab} contains the Matlab code used to calculate the cable length.

%tasks 3, 4 and 5
\inputfrom{../../deliverable-5-radar/}{tasks-3-4-5}
\end{document}